---
title: "antibioticos"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(plyr)
library( reshape )

```

## Presence of antibiotic genes in BGCs 


Methodology
Families of CARD
Homology search was conducted using blast (e-vaule )all vs all were Antibiotic resistance genes from The Comprehensive Antibiotic Resistance Database (CARD) where blasted all vs all 
FastOrtho 

Homology searches between CARD and MIBiG 
blast CARD vs MiBIG
blast MiBiG bs CARD

¿How many BGCs contain an AR gene?
¿How many families of AR genes are present in BGC?
Which families are over represented
How many BGCs per AR gene/Family

```{r cars}
file="CARD.FO.families"


CARDFamiliesTable <- read_delim(file, "\t", escape_double = FALSE, col_names = FALSE, trim_ws = TRUE)
head(CARDFamiliesTable)
#Familia1 numDominios
#Cada renglón es una ocurrencia de un gen de la familia 1
#colnames(FIRSTmissionTable)=c("family","domains_number")
#FIRSTmissionTable$Ordenado<-factor(FIRSTmissionTable$family, unique(as.character(FIRSTmissionTable$family)))
#p<-ggplot(FIRSTmissionTable,aes(x=Ordenado,y=domains_number,fill=family))+geom_boxplot(outlier.shape = NA)+geom_jitter(width=0.28,alpha=0.028)+xlab("Gene families")+ylab("Number of domains")+theme(axis.text.x = element_text(size = 6))+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),legend.position = "none",panel.background = element_rect(fill = "white",colour = "grey50"))
#p
#p+theme(plot.margin = unit(c(1,1,1.5,1.2),"cm"))
#ggsave("DomainDistro1-20first.svg",plot = p,width=30,height = 15,units = "cm")
```
